Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids

### 2024-02-22 NovelLBM.tex
workaround closes #7 closes #8

@@

We start by simulating the alginate and \SI{0.49}{\percent} methyl cellulose solutions with a viscosity ratio $R_\eta = \num{48.2e3}$ and $R_\eta = \num{18.7}$, respectively, in 2D planar Poiseuille flow.
In physical units the channel has a height of \SI{20}{\micro\meter} which are discretized with 41 \SG{ XX }\RK{pipe is 41 box is 43} LBM nodes.
For the viscosity shuffling, we set $\alpha_\text{s} = 1$.
Along the flow direction, the channel is periodic, and the flow is driven by a pressure gradient of \SI{-1e7}{\pascal\per\meter} for alginate and  approximately \SI{-1.2e7}{\pascal\per\meter} for methyl cellulose. \SG{ pressure for MC? }\RK{done}
\RK{
	2D Param (MC) -12459373.981063413
	3D Param (MC) -24918747.962126825
	2D Alg -1e7
	3D Alg -2e7
}
The velocity field is initialized with zero.
For methyl cellulose, we simulate the full temporal evolution with the polymers starting in the unstretched configuration.
In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched \SG{ give details }\RK{initialized to the semianalytical solution}.
After \num{2e9} LBM time steps for alginate and \num{5e6} LBM time steps for methyl cellulose \SG{ XX }\RK{done} corresponding to approximately \SI{1.6}{\milli\second} and \SI{2.4}{\second} \SG{ XX }\RK{done} of physical time respectively, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
\RK{
	Alg 2e9 1.6455647956111251 ms (reveals the sim to be a scam)
	MC 5e6 2.439024390243903 s
}
As shown in figure~\ref{fig:2Dvel}, very good agreement is found.
For a quantitative assessment, we compute the L2 error as follows.
\begin{equation}
	e_\text{L2} = \sqrt{\frac{\sum_i\left[\vec{u_i} - \vec{u}\left(y_i\right)\right]^2}{\sum_i\vec{u}\left(y_i\right)^2}}
\end{equation}
\SG{ give correct equn. }\RK{done}

>>>>

% Workaround we have to use because some people cannot be expected to update their packages more often than once a decade
% https://tex.stackexchange.com/a/612592
% This is technically licenced under CC BY-SA 4.0
\ifdefined\qty\else
\ifdefined\NewCommandCopy
\NewCommandCopy\qty\SI
\else
\NewDocumentCommand\qty{O{}mm}{\SI[#1]{#2}{#3}}
\fi
\fi
\ifdefined\unit\else
\ifdefined\NewCommandCopy
\NewCommandCopy\unit\si
\else
\NewDocumentCommand\unit{O{}m}{\si[#1]{#2}}
\fi
\fi

@@

We start by simulating the alginate and \SI{0.49}{\percent} methyl cellulose solutions with a viscosity ratio $R_\eta = \num{48.2e3}$ and $R_\eta = \num{18.7}$, respectively, in 2D planar Poiseuille flow.
In physical units the channel has a height of \SI{20}{\micro\meter} which are discretized with 41 \SG{ XX }\RK{pipe is 41 box is 43} LBM nodes.
For the viscosity shuffling, we set $\alpha_\text{s} = 1$.
Along the flow direction, the channel is periodic, and the flow is driven by a pressure gradient of \SI{-1e7}{\pascal\per\meter} for alginate and  approximately \SI{-1.2e7}{\pascal\per\meter} for methyl cellulose. \SG{ pressure for MC? }\RK{done}
\RK{
	2D Param (MC) -12459373.981063413
	3D Param (MC) -24918747.962126825
	2D Alg -1e7
	3D Alg -2e7
}
The velocity field is initialized with zero.
For methyl cellulose, we simulate the full temporal evolution with the polymers starting in the unstretched configuration.
In the case of alginate, we speed up the convergence and start from a situation in which the polymers are pre-stretched \SG{ give details }\RK{initialized to the semianalytical solution}.
After \num{2e9} LBM time steps for alginate and \num{5e6} LBM time steps for methyl cellulose \SG{ XX }\RK{done} corresponding to approximately \SI{1.6}{\milli\second} and \SI{2.4}{\second} \SG{ XX }\RK{done} of physical time respectively, the simulation is stopped and the flow field $u(y)$ is compared to the semi-analytical solution.
\RK{
	Alg 2e9 1.6455647956111251 ms (reveals the sim to be a scam)
	MC 5e6 10.065719379854297 ms
}
As shown in figure~\ref{fig:2Dvel}, very good agreement is found.
For a quantitative assessment, we compute the L2 error as follows.
\begin{equation}
	e_\text{L2} = \sqrt{\frac{\sum_i\left[\vec{u_i} - \vec{u}\left(y_i\right)\right]^2}{\sum_i\vec{u}\left(y_i\right)^2}}
\end{equation}
\SG{ give correct equn. }\RK{done}
